New Biomass Pools Workflow

### 2023-10-05 NewBiomassPoolsWorkflow.Rmd
run truth works now, om_init works too

@@

In `om_species` need to check for biomass pools output and append that to the `truebio_ss` object? If one object can use existing `om_index` on bio pools.

@@

If a single true bio object is created, may have to modify selectivty definition for biomass pools in `om_index`

>>>>

Testing--have to ask for N data for only biomass pool groups. If there are none we should trap this.

```{r, eval=FALSE}

dir <- here("atlantisoutput","NOBA_sacc_30")
file_fgs <- "nordic_groups_v04.csv"
biomass.pools.file <- "nordic_biol_v23.nc"
file_biolprm <- "nordic_biol_incl_harv_v_011_1skg.prm"
file_bgm <- "Nordic02.bgm"
file_init <- "nordic_biol_v23.nc"
file_runprm <- "nordic_run_v04.xml"
scenario <- "nordic_runresults_01"
verbose <- TRUE
annage <- TRUE
file_fish <- "NoBAFisheries.csv"

  # Read in information
  # Read in the functional groups csv since that is used by many functions
  fgs <- load_fgs(dir = dir, file_fgs = file_fgs)

    #Get just the names of active functional groups
  funct.group.names <- fgs %>%
    filter(IsTurnedOn == 1) %>%
    select(Name) %>%
    .$Name

  select_groups <- funct.group.names

  # Read in the biomass pools
  bps <- load_bps(dir = dir, fgs = file_fgs, file_init = file_init)
  # Read in the biological parameters
  biol <- load_biolprm(dir = dir, file_biolprm = file_biolprm)
  # Read in the run parameters
  runprm <- load_runprm(dir = dir, file_runprm = file_runprm)

  nc_catch <- paste0(scenario, 'CATCH.nc')
  dietcheck <- paste0(scenario, 'DietCheck.txt')
  nc_out <- paste0(scenario, ".nc")
  nc_prod <- paste0(scenario, "PROD.nc")
  file_catchfish <- file.path(dir,
    paste0(scenario, "CatchPerFishery.txt"))
  file_catch <- paste0(scenario, "Catch.txt")

  if(annage){
    if(!file.exists(paste0(file.path(dir,paste0(scenario, 'ANNAGEBIO.nc'))))){
      stop("ANNAGEBIO.nc file not found")
    }
    if(!file.exists(paste0(file.path(dir,paste0(scenario, 'ANNAGECATCH.nc'))))){
      stop("ANNAGECATCH.nc file not found")
    }
    nc_annagebio <- paste0(scenario, 'ANNAGEBIO.nc')
    nc_annagecatch <- paste0(scenario, 'ANNAGECATCH.nc')
  }

  # Get the boundary boxes
  allboxes <- load_box(dir = dir, file_bgm = file_bgm)
  boxes <- get_boundary(allboxes)

  # Get box area for benthic biomass pool calc
  area <- load_boxarea(dir = dir,
                       file_bgm = file_bgm)

  #Extract from NetCDF files
  # Need: dir, file_nc, bps, fgs, select_groups, select_variable,
  # check_acronyms, bboxes

  nums <- load_nc(dir = dir,
                  file_nc = nc_out,
                  bps = bps,
                  fgs = fgs,
                  select_groups = select_groups,
                  select_variable = "Nums",
                  check_acronyms = TRUE,
                  bboxes = boxes)
  if(verbose) message("Numbers read in.")

  resn <- load_nc(dir = dir,
                  file_nc = nc_out,
                  bps = bps,
                  fgs = fgs,
                  select_groups = select_groups,
                  select_variable = "ResN",
                  check_acronyms = TRUE,
                  bboxes = boxes)
  if(verbose) message("Reserve nitrogen read in.")

  structn <- load_nc(dir = dir,
                  file_nc = nc_out,
                  bps = bps,
                  fgs = fgs,
                  select_groups = select_groups,
                  select_variable = "StructN",
                  check_acronyms = TRUE,
                  bboxes = boxes)
  if(verbose) message("Structural nitrogen read in.")

  eat <- load_nc(dir = dir,
                     file_nc = nc_prod,
                     bps = bps,
                     fgs = fgs,
                     select_groups = select_groups,
                     select_variable = "Eat",
                     check_acronyms = TRUE,
                     bboxes = boxes)
  if(verbose) message("Eaten read in.")

  grazing <- load_nc(dir = dir,
                 file_nc = nc_prod,
                 bps = bps,
                 fgs = fgs,
                 select_groups = select_groups,
                 select_variable = "Grazing",
                 check_acronyms = TRUE,
                 bboxes = boxes)
  if(verbose) message("Grazing read in.")

  vol <- load_nc_physics(dir = dir,
                         file_nc = nc_out,
                         physic_variables = "volume",
                         aggregate_layers = FALSE,
                         bboxes = boxes)
  if(verbose) message("Volume read in.")

  # biomass pools added 2023 for Rpath testing
  pools <- fgs %>%
    dplyr::filter(NumCohorts == 1,
                  IsTurnedOn == 1) %>%
    dplyr::select(Name) %>%
    .$Name

  pooln <- load_nc(dir = dir,
                   file_nc = nc_out,
                   bps = bps,
                   fgs = fgs,
                   select_groups = pools,
                   select_variable = "N",
                   check_acronyms = TRUE,
                   bboxes = boxes)
 if(verbose) message("Biomass pools N read in.")

@@

In `om_species` need to check for biomass pools output and append that to the `truebio_ss` object? If one object can use existing `om_index` on bio pools. However, will that be a problem if trying to combine the truenums and truebio objects? They won't be the same length. Perhaps leave separate at this level and combine only if needed.

@@

If a single true bio object is created, may have to modify selectivty definition for biomass pools in `om_index`. If left separate can apply no selectivity to biomass pool groups, only efficiency.
